master thesis

### 2018-03-18 Paper - Latex/Paper - Skizze - v4.tex
Paper - Results - Results of simulation

    \begin{figure}[h!]
      \centering
      \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=0.8\textwidth]{Figures/simulation_evaluation_1.png}
      \caption{Influence of unknown data to prediction}
    \end{figure}

>>>>

      As presented, we compare two methods in our simulation to their prediction accuracy: Fitch and 
        Sankoff. \\
      We examine different parameters. In figure \ref{fig:influence of unknown data} is an overview of 
        the results. \\
      The first column describes the distributions of free-livings and parasites with a given threshold 
        for the respective simulations to the right. \\
      The middle column investigates the influence of the unknown states, the right the influence of the 
        strength of the multifurcation. \\
      The y-axes indicate the percentage of correctly predicted states (including known states). On the 
        x-axis the percentage of forgotten states or missing internal nodes. \\
      Each point corresponds to the average of one hundred simulations, each with 10,000 leaf nodes. \\
      For the middle column we set the strength of the multifurcations to 0.95\% similar to the real 
        data and in the right column the amount of the unknowns to 0.95\% also similar to the real data. \\

      As you can see both algortithms are always over 50\% and therefore better than guessing. Moreover, 
        they are usually close to each other, with Sankoff always makes better predictions except for 
        equally distributed states as Fitch. \\
      You can see that the distribution of states has a strong influence on the prediction. The more 
        evenly distributed, the harder it is to predict. \\
      If more than 60\% of internal nodes are missing, Fitch breaks significantly in his prediction 
        compared to Sankoff.

      \begin{figure}
        \centering
        \includegraphics[trim = 0mm 0mm 0mm 0mm, clip,width=\textwidth]{Figures/simulation_evaluation_1.png}
        \caption{Influence of unknown data to prediction}
        \label{fig:influence of unknown data}
      \end{figure}

      In the end, Sankoff is in most cases the more accurate algortihmus and was therefore used for our 
        prediction of the real data.
